Learning Useful Changes\\(to Reduce Runtimes and Software Defects)

### 2015-08-20 Manuscript.tex
Updates from ShareLaTeX

 This paper uses these learners to learn methods
 to reduce defects and decrease program runtime.
 For the test data of this paper, those improvements   reduce
 the expected values of defect counts and  runtimes to    
 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
We propose a novel {\em planning} approach called CROSSTREES for learning changes to a software system
such that its performance ``improvess'', according to some measure. For  casew
stuides, we apply CROSSTREES to   (1)~reducethe predicted number
of defects and (2)~reduce the runtimes of five system.

>>>>

 This paper uses these learners to learn methods
 to reduce defects and decrease program runtime.
 For the test data of this paper, those improvements   reduce
 the expected values of defect counts and  runtimes to    
 45\%,\%  (median) and 66\%,20\% (best case) of the initial values, respectively.
\end{abstract}
\section{Introduction}
We propose a novel {\em planning} approach called CROSSTREES for learning changes to a software system
such that its performance ``improves'', according to some measure. For  case 
studies, we apply CROSSTREES to   (1)~reduce the predicted number
of defects and (2)~reduce the runtimes of five system.
